Dynamic Transition Analysis with TIMES

### 2020-12-10 doc/2020-03-paper/Appendix.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

\section{Model data, assumptions, and secondary results} \label{Appendix}

\begin{table}[H]
	\caption{Data for initial condition.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{Coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

\begin{figure}[h] 
\centering
\label{ic-elc}
\includegraphics[scale=0.5]{figures/IC}
\caption{Electricity generation that defines the initial condition of the model.}
\end{figure}

@@

	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}

@@

\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\

@@

\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
 & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\

@@

Li-ion Storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\

@@

Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\

@@

Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\

@@

Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\

@@

Gas Reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\

@@

Gas Reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\

@@

\begin{table}[H]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[H]
%\begin{minipage}{\textwidth} 
	\caption{Capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Max. Annual} \\
  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
Onshore Wind \cite{irena_renewable_2020} & 25\% \\
Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion Storage & 30\% \\
Natural Gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

@@

\subsection{Sensitivity analysis secondary results}

>>>>

\section{Model data and assumptions} \label{Appendix}

\begin{table}[H]
	\caption{Data for defining the initial condition across all simulations.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

\begin{figure}[h] 
\centering
\label{ic-elc}
\includegraphics[scale=0.5]{figures/IC}
\caption{Electricity generation between 2013-2016 that defines the initial condition across all simulations.}
\end{figure}

@@

	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}

@@

\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\

@@

\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity factor/} & \textbf{Emission} & \textbf{Year} \\
 & \textbf{cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{efficiency} & \textbf{coefficient} & \textbf{available} \\
 & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\

@@

Li-ion storage \cite{mongird_energy_2019,emilsson_lithium-ion_2019} & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 151(2017) & 2017 \\

@@

Onshore wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\

@@

Offshore wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\

@@

Offshore wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\

@@

Gas reforming  & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 356.6 & 2022\\

@@

Gas reforming-CCS(70\%) & 1200 & 8 & 0.065 & 30 & Eff=0.56 & 179 & 2022\\

@@

\begin{table}[H]
	\caption{Nameplate capacity deployment limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[H]
%\begin{minipage}{\textwidth} 
	\caption{Nameplate capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Maximum Annual Growth Rate} \\
%  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and emerging solar \cite{irena_renewable_2020} & 40\%  \\
Onshore wind \cite{irena_renewable_2020} & 25\% \\
Offshore wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion storage & 30\% \\
Natural gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

@@

\section{Sensitivity analysis secondary results}

### 2020-12-10 doc/2020-03-paper/abstract.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model. Key features of our simulations include the incorporation of novel technologies, like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emission and learning curves for technology costs and emission coefficients. Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security. Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.

>>>>

We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model. Key features of our simulations include the incorporation of novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, long-term impact assessment up to the year 2100, the inclusion of life-cycle emissions, and learning curves for parameters such as investment cost, efficiency, and emission coefficient. Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security. Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.

### 2020-12-10 doc/2020-03-paper/acros.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba
minor corrections
Former-commit-id: 73fa67ae7dfdd55dc9ca0475bcfdd9cec707fa25
Former-commit-id: 37a6fe9c80ddc0b9080cf1e4d4e034e7c6c4cdd7
lit review corrections
Former-commit-id: 4f44fc931963a354bcb5e74b1219f87f407636f2
Former-commit-id: 249f1c80ef74feb3134bb71a245fda4f1a107c33
NP edits to abstract, intro, litreview
Former-commit-id: 5795136ab0425b3098421689e04c60f182ee9eeb
Former-commit-id: 3c46b1f96b7953ed01d26a4a60f7536106eff12e
NP edits to sections 3-app

\newacronym{<++>}{<++>}{<++>}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon Neutral Energy Research}
\newacronym{MARKAL}{MARKAL}{MARKet ALlocation}
\newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
\newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
\newacronym{USC}{USC}{Ultra Supercritical Coal}
\newacronym{OM}{O\&M}{Operation and Maintenance Cost}
\newacronym{PEMFC}{PEM Fuel Cells}{Polymer Electrolyte Membrane Fuel Cells}
\newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
\newacronym{lng}{LNG}{Liquified Natural Gas}
%\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

>>>>

\newacronym{<++>}{<++>}{<++>}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon Neutral Energy Research}
\newacronym{MARKAL}{MARKAL}{MARKet ALlocation}
\newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
%\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
\newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
\newacronym{CCS}{CCS}{carbon capture and sequestration}
\newacronym{USC}{USC}{ultra-supercritical coal}
\newacronym{OM}{O\&M}{operation and maintenance}
\newacronym{PEMFC}{PEMFC}{polymer electrolyte membrane fuel cell}
\newacronym{lcoe}{LCOE}{levelized cost of electricity}
\newacronym{lng}{LNG}{liquified natural gas}
\newacronym{AEC}{AEC}{alkaline electrolyser cell}
\newacronym{PEMEC}{PEMEC}{polymer electrolyte membrane electrolyser cell}
\newacronym{SOEC}{SOEC}{solid oxide electrolyser cell}
\newacronym{SOFC}{SOFC}{solid oxide fuel cell}
\newacronym{PWS}{PWS}{photochemical water splitting}
\newacronym{INDC}{INDC}{Intended Nationally Determined Contribution}
\newacronym{GHG}{GHG}{greenhouse gas}
\newacronym{BOP}{BOP}{balance of plant}
\newacronym{P2G}{P2G}{power-to-gas}
\newacronym{FCV}{FCV}{fuel cell vehicle}
%\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-12-10 doc/2020-03-paper/introduction.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

\section{Introduction} \label{Introduction}
In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalized this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from largely from energy consumption of the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions. However these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid). Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. This vagueness may be due to uncertainty regarding the economical feasibility of GHG emissions reduction in each sector. It has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delayed action in preference for future technologies \cite{ashina_roadmap_2012}. It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in the hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimizing the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonization pathways that meet the increasing near-term electricity demand. Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

>>>>

\section{Introduction} \label{Introduction}
In order to mitigate climate change, and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from largely from energy consumption of the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. For developed economy nations rich in natural resources, switching to natural gas or implementing \gls{CCS} on fossil fuel plants is one option to reduce GHG emissions. However, these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. For Japan, a developed nation without fossil fuel resources, the challenge to reduce GHG emissions is likely to follow a different path, already evidenced by the restart of nuclear reactors and a shift toward large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarised as '3E+S'; ibid). Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. This vagueness may be due to uncertainty regarding the economic feasibility of GHG emissions reduction in each sector. It has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in the hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

The aim of this research is to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand. Additionally, the significance of key economic parameters of emerging technologies is assessed through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2020-12-10 doc/2020-03-paper/litreview.tex
NP edits to sections 3-appendix
Former-commit-id: 45551a7116ca965f165eb7d011a24b05378da87c
Former-commit-id: ddc9a8a9d45bb5fdd28261143754afd7f5f91e95

The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modeling approaches. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognizing the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan. Their study identified that \gls{P2G} can increase the effective utilization rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid aging, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets. Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modeling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonizes a number of modeling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilizing national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognize the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \glspl{FCV} and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realize low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalize regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritize research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research are unique, as they build on the modeling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and operation and maintenance (O\&M) costs, efficiency, and emission coefficients. Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modeling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

>>>>

The Paris Agreement commits individual nations to significant carbon reduction over time through the Intended Nationally Determined Contribution (INDC) mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the "development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Aware of these targets, a number of authors have evaluated Japan's future energy system using a variety of modelling approaches. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through \gls{P2G} approaches in Kyushu, Japan. Their study identified that \gls{P2G} can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid aging, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets. Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight \glspl{FCV} and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research are unique, as they build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model also incorporates life-cycle emissions of all conventional and emerging technologies, which are typically neglected externalities. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.
